\pkg{disaggregation}: An \proglang{R} Package for Bayesian Spatial Disaggregation Modelling

### 2020-02-25 article.Rnw
Tiny edits

# Running the MCMC algorithm - takes a long time
start <- Sys.time()
mcmc_out <- tmbstan(model_object, chains = 4, iter = 8000, warmup = 2000,
                    cores = getOption('mc.cores', 4))
end <- Sys.time()
print(end - start)

# Plot the trace of the parameter values
stan_trace(mcmc_out, 
           pars = c('intercept', 
                    'slope[1]', 'slope[2]', 'slope[3]', 'slope[4]', 
                    'iideffect_log_tau', 'log_sigma', 'log_rho'))
@
%

@@

The results in this paper were obtained using
\proglang{R}~\Sexpr{paste(R.Version()[6:7], collapse = ".")} with the
\pkg{TMB}~\Sexpr{packageVersion("TMB")} package. \proglang{R} itself
and all packages used are available from the Comprehensive
\proglang{R} Archive Network (CRAN) at
\url{https://CRAN.R-project.org/}, apart from \pkg{INLA}, which can be 
installed in \proglang{R} using the command:
%
<<inla, eval=FALSE>>=
install.packages("INLA", 
                 repos = c(getOption("repos"), 
                           INLA="https://inla.r-inla-download.org/R/stable"), 
                 dep=TRUE)
@
%

>>>>

start <- Sys.time()
mcmc_out <- tmbstan(model_object, chains = 4, iter = 8000, warmup = 2000,
                    cores = getOption('mc.cores', 4))
end <- Sys.time()
print(end - start)

stan_trace(mcmc_out, 
           pars = c('intercept', 
                    'slope[1]', 'slope[2]', 'slope[3]',
                    'iideffect_log_tau', 'log_sigma', 'log_rho'))
@
%

@@

The results in this paper were obtained using
\proglang{R}~\Sexpr{paste(R.Version()[6:7], collapse = ".")} with the
\pkg{TMB}~\Sexpr{packageVersion("TMB")} package. \proglang{R} itself
and all packages used are available from the Comprehensive
\proglang{R} Archive Network (CRAN) at
\url{https://CRAN.R-project.org/}, apart from \pkg{INLA}, which can be 
installed in \proglang{R} using the command:
%
<<inla, eval=FALSE>>=
install.packages("INLA", 
                 repos=c(getOption("repos"), 
                         INLA="https://inla.r-inla-download.org/R/stable"), 
                 dep=TRUE)
@
%
